% T I T L E   P A G E
% -------------------
% Last updated June 14, 2017, by Stephen Carr, IST-Client Services
% The title page is counted as page `i' but we need to suppress the
% page number. Also, we don't want any headers or footers.
\pagestyle{empty}
\pagenumbering{roman}


% The contents of the title page are specified in the "titlepage"
% environment.
\begin{titlepage}
    \begin{center}
        \vspace*{1.0cm}

        \Huge Mean Field Behaviour of Job Redundancy Queueing Models

        \vspace*{1.0cm}

        \normalsize
        by \\

        \vspace*{1.0cm}

        \Large
        Aaron Janeiro Stone \\

        \vspace*{3.0cm}


    \end{center}
\end{titlepage}

% The rest of the front pages should contain no headers and be numbered using Roman numerals starting with `ii'
\pagestyle{plain}
\setcounter{page}{2}

\cleardoublepage % Ends the current page and causes all figures and tables that have so far appeared in the input to be printed.
% In a two-sided printing style, it also makes the next page a right-hand (odd-numbered) page, producing a blank page if necessary.


% D E C L A R A T I O N   P A G E


\bigskip

\noindent
I understand that my thesis may be made electronically available to the public.

\cleardoublepage

% A B S T R A C T
% ---------------

\begin{center}
    \textbf{Abstract}
\end{center}
Technological advancement in cloud computing has resulted in the viability of a new class of
routing algorithm, the so-called redundancy models which are able to replicate jobs for processing on different
servers. An asymptotic amount of queue-endowed servers could in this way employ their plentiful, otherwise
idle servers towards processing.
Research on the behaviour of such systems, however, has only conjectured
the asymptotic independence of queues (Gardner, Harchol-Balter, \& Scheller-Wolf, 2016; Hellemans, Bodas,
\& Van Houdt, 2019).
To this end, by modelling the process as a time-indexed family of hypergraphs wherein
hyperedges represent cloned dependents,  along with the notion of exchangeable
random groups derived by Austin (2008), we are able to demonstrate the conjectured behaviour in a simulation setting.

\cleardoublepage

% A C K N O W L E D G E M E N T S
% -------------------------------

\begin{center}
    \textbf{Acknowledgements}
\end{center}
Thank you, Dr. Steve Drekic and Dr. Tim Hellemans, for your guidance as I delved into an area once foreign to me.

\cleardoublepage

% D E D I C A T I O N
% -------------------

\begin{center}
    \textbf{Dedication}
\end{center}

Thank you, Fatima and my family, for always being there for me in such a fast-moving world.

\quad

\textit{The whole entire world is a very narrow bridge; the main thing is to have no fear at all.}
\flushright - \textit{Nachman}
\flushleft
\cleardoublepage

% T A B L E   O F   C O N T E N T S
% ---------------------------------
\renewcommand\contentsname{Table of Contents}
\tableofcontents
\cleardoublepage
\phantomsection    % allows hyperref to link to the correct page

% L I S T   O F   T A B L E S
% ---------------------------
%\addcontentsline{toc}{chapter}{List of Tables}
%\listoftables
%\cleardoublepage
%\phantomsection		% allows hyperref to link to the correct page

% L I S T   O F   F I G U R E S
% -----------------------------
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\cleardoublepage
\phantomsection        % allows hyperref to link to the correct page


% Change page numbering back to Arabic numerals
\pagenumbering{arabic}

